Succinct representations for abstract interpretation

### 2011-11-02 papers/PLDI2012/implicitization.tex
typo

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. 
Since we dynamically construct these functions
during the analysis, we store their already comupted image into a
compact representation, such as Algebraic Decision Diagrams.
$\sigma_i(j,k)$ is then constructed on the fly only when needed, and computed
only once.
When the value of $\sigma_i(j,k)$ is required but undefined, we first compute
the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		%\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		%d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}
The main difference with the original
algorithm~\cite{DBLP:conf/pldi/GulwaniZ10} is that we construct
$\sigma_i(j,k)$ using SMT queries instead of enumerating a possibly
exponential number of paths to find a solution.

>>>>

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. 
Since we dynamically construct these functions
during the analysis, we store their already computed image into a
compact representation, such as Algebraic Decision Diagrams.
$\sigma_i(j,k)$ is then constructed on the fly only when needed, and computed
only once.
When the value of $\sigma_i(j,k)$ is required but undefined, we first compute
the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		%\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		%d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}
The main difference with the original
algorithm~\cite{DBLP:conf/pldi/GulwaniZ10} is that we construct
$\sigma_i(j,k)$ using SMT queries instead of enumerating a possibly
exponential number of paths to find a solution.
